---
---
title: "Unit05"
author: "Josie McDaniel"
date: "October 9, 2017"
output: 
  html_document:
    keep_md: True
---

# 1a. import a text file include the column name

```{r}
df <- read.table("C:/Users/dk49581/Desktop/MSDS Homework/Unit05/yob2016.txt", sep=";", col.name=c("Name", "Gender", "2016 Total"))
```


#1b.  display the summary and structure of the text file

```{r}
summary (df)
str(df)
```

#1c. find and display the one misspelled name with three ys

```{r}
dfSubset <- df[grep("yyy", df$Name), ]
dfSubset
```

#1d. removed the misspelled name and create a new file 

```{r}
y2016 <- subset(df, Name !='Fionayyy')
head(y2016, n=215)
```

#2a. Import .txt file y2015
```{r, echo=TRUE}
y2015 <- read.table("C:/Users/dk49581/Desktop/MSDS Homework/Unit05/yob2015.txt", sep=",", col.name=c("Name", "Gender", "2015 Total"))
```

#2b.  display the last ten rows.  The last 10 rows contains all males and there are 5 children in 2015 with those names

```{r, echo=TRUE}
tail(y2015, n=10)
```

#2c.  merge y2016 and y2015 by Name column and name it final.  name that are in both 2016 and 2016 without NA value in amount of children

```{r, echo=TRUE}
final <- merge(y2015, y2016, by = "Name", na.rm = TRUE, all=FALSE)
```

#3a create a new column called Total which the amount of children in 2015 and 2016 and then a column total
```{r, echo=TRUE}
final$Total <- final$X2015.Total+final$X2016.Total
```

#3b Sort by Total and display top 10 names
```{r, echo=TRUE}
newdata <- final[order(final$Total),] 
tail(newdata, n=10)
```

#3c display top 10 girl F names
```{r, echo=TRUE}
newer <- df[which(newdata$Gender.x == "F"),]
newer <- newer[order(newer$Gender),] 
newer <-head(newer, n=10)
```
 
#3d write out top 10 girl names and their totals to a CSV file..  no other columns
```{r, echo=TRUE}
newer <- subset( newer, select = -Gender )
write.csv(newer, file = "C:/Users/dk49581/Desktop/MSDS Homework/Unit05/MyData.csv")
```

#4 Push the Rmarkdown and a Codebook to Github repositories

